Efficient Machine Learning Approaches for Fast Risk Evaluation of VAs

### 2025-01-03 pre_private/pre.tex
we

Key ideas: 
\begin{itemize}
    \item Pool inner replications from different outer scenarios 
    \item Use metamodeling techniques to approximate the inner simulation model
\end{itemize}

@@

\begin{frame}{Introduction}

    \begin{figure}[H]
        \makebox[\textwidth][c]{
            \subfigure{
                \begin{tikzpicture}[scale=0.7]
                \draw[-latex] (0,0)--(2,0);
                \draw[-latex] (2.2,0)--(4,2) node[right]  {$\blacksquare$};
                \draw[-latex] (2.2,0)--(4,0.5) node[right]  {$\blacksquare$};
                \draw[-latex] (2.2,0)--(4,-2) node[right]  {$\blacksquare$};
                \node at (1.2,-0.3) {$X_i$};
                \node at (3.8,-0.7) {$\vdots$};
                \node at (4.2,-0.7) {$\vdots$};
                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (4.5,2.2) --  (4.5,-2.2);
                \node at (5.3,0) {$\hat L_i$};
                \node at (2,-3.1) {1 Outer Path in standard SPNS};
                \end{tikzpicture}}
            \subfigure{
                \begin{tikzpicture}[scale=0.6]
                \draw[-latex] (0,0)--(10,0);
                \draw[-latex] (0,0)--(-1,1.5) node[above] {$\blacksquare$};
                \draw[-latex] (0,0)--(0,1.5) node[above] {$\blacksquare$};
                \draw[-latex] (0,0)--(1,1.5) node[above] {$\blacksquare$};
                \node at (0.5,1.2) {\small$\dots$};
                \node at (0.5,1.85) {\small$\dots$};

@@

                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (-1,2) --  (1,2);
                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (2,2) --  (4,2);
                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (5,2) --  (7,2);
                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (8,2) --  (10,2);
                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=12pt}] (0,2.4) --  (9,2.4);
                \node at (4.5,-0.5) {$X_i$};
                \node at (4.5,3.5) {$\hat L_i$};
                \node at (4.5,-1.3) {1 Outer Path in standard MPNS};
                \end{tikzpicture}
                }}
	\end{figure}

    Metamodeling: think of the inner simulation as a black-box function.

>>>>

\textbf{Key ideas:} 
\begin{itemize}
    \item Pool inner replications from different outer scenarios 
    \item Use metamodeling techniques to approximate the inner simulation model
\end{itemize}

@@

\begin{frame}{From Options to Variable Annuities}

    Variable annuities (VAs) poses a challenge for nested simulation due to its \textbf{high-dimensional} and \textbf{complex payoff structure}.

    \begin{figure}[H]
        \makebox[\textwidth][c]{
            \subfigure{
                \begin{tikzpicture}[scale=0.7]
                \draw[-latex] (0,0)--(2,0);
                \draw[-latex] (2.2,0)--(4,2) node[right]  {$\blacksquare$};
                \draw[-latex] (2.2,0)--(4,0.5) node[right]  {$\blacksquare$};
                \draw[-latex] (2.2,0)--(4,-2) node[right]  {$\blacksquare$};
                \node at (1.2,-0.3) {$S_i$};
                \node at (3.8,-0.7) {$\vdots$};
                \node at (4.2,-0.7) {$\vdots$};
                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (4.5,2.2) --  (4.5,-2.2);
                \node at (5.3,0) {$\hat L_i$};
                \node at (2,-3.1) {1 Outer Path for Options};
                \end{tikzpicture}}
            \subfigure{
                \begin{tikzpicture}[scale=0.6]
                \draw[-latex] (0,0)--(10,0);
                \draw[-latex] (0,0)--(-1,1.5) node[above] {$\blacksquare$};
                \draw[-latex] (0,0)--(0,1.5) node[above] {$\blacksquare$};
                \draw[-latex] (0,0)--(1,1.5) node[above] {$\blacksquare$};
                \node at (0.5,1.2) {\small$\dots$};
                \node at (0.5,1.85) {\small$\dots$};

@@

                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (-1,2) --  (1,2);
                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (2,2) --  (4,2);
                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (5,2) --  (7,2);
                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=5pt}] (8,2) --  (10,2);
                \draw [decorate,  decoration = {brace,    raise=1pt,    amplitude=12pt}] (0,2.4) --  (9,2.4);
                \node at (4.5,-0.5) {$S_i$};
                \node at (4.5,3.5) {$\hat L_i$};
                \node at (4.5,-1.3) {1 Outer Path for VAs};
                \end{tikzpicture}
                }}
	\end{figure}

    \begin{itemize}
        \item Need to reconstruct a metamodeling-based nested simulation procedure
    \end{itemize}

\begin{frame}{Nested Simulation for VAs}

    \begin{figure}[c]
        \includegraphics[width=\textwidth]{../project2/figures/sns.pdf}
        \caption{Illustration of nested simulation that estimates the P\&L for one outer scenario}
    \end{figure}
